---
title: "Tutorial_PS1"
author: "Donovan Doyle"
date: "2/18/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(readxl)
library(knitr)
library(kableExtra)
library(stringr)
library(taRifx)
```

#Question 5
```{r read-in, echo = FALSE}
unzip("ps1.zip")

irs <- read.csv("ps1/rawdata/irs2015.csv", stringsAsFactors = FALSE)
str(irs)
irs2015narrow <- irs %>%
  select(year, state, zip5, cz, cz_name, bin, returns, agi, wages_amount, interest_amount,
dividends_ordinary_amount, dividends_qualified_amount, capgains_amount,
contrib_amount) %>%
  filter(agi != "**") %>%
  filter(wages_amount != "**") %>%
  filter(interest_amount != "**") %>%
  filter(dividends_ordinary_amount != "**") %>%
  filter(dividends_qualified_amount != "**") %>%
  filter(capgains_amount != "**") %>%
  filter(contrib_amount != "**") %>%
  filter(returns != "**") %>%
  mutate(agi = parse_number(agi)) %>%
  mutate(wages_amount = parse_number(wages_amount)) %>%
  mutate(interest_amount = parse_number(interest_amount)) %>%
  mutate(dividends_ordinary_amount = parse_number(dividends_ordinary_amount)) %>%
  mutate(dividends_qualified_amount = parse_number(dividends_qualified_amount)) %>%
  mutate(capgains_amount = parse_number(capgains_amount)) %>%
  mutate(contrib_amount = parse_number(contrib_amount)) %>%
  mutate(returns = parse_number(returns))

glimpse(irs2015narrow)
```

# Question 6
```{r q6, echo = FALSE}
(irs2015_6 <- irs2015narrow %>%
  mutate(agi_per_return = agi / returns) %>%
  filter(state == "ma") %>%
  select(agi_per_return) %>%
  summary())
```


# Question 7
```{r q7, echo = FALSE}
irs2015_allreturns <- irs2015narrow %>%
  filter(bin == "All") %>%
  as.tibble()
```


# Question 8
#For drawing the map (only has to be done once)
install.packages("devtools")
library(devtools)
install_github('arilamstein/choroplethrZip@v1.5.0')
## load libraries
library(choroplethrZip)
##Prep data for map: region (zip code) in one column and value (AGI/return) in second
#Create variable "value" = agi_per_return
irs2015_allreturns$value <- irs2015_allreturns$agi_per_return
# Create variable "region" = zip5
# These functions convert to character from numeric and add leading 0s to zips like 02138
irs2015_allreturns$region <- as.character(irs2015_allreturns$zip5)
irs2015_allreturns$region <- str_pad(irs2015_allreturns$region, 5, pad = "0")
agi_per_zip5 <- select(irs2015_allreturns, region, value)
#Define Boston CZ by listing all the county FIPS codes for the counties in Boston CZ
ic_cz = c(19103, 19031, 19095, 19183, 19111, 19139, 19113)
#Draw map using zip_choropleth function
choro_agi_per_return = zip_choropleth(agi_per_zip5,
 title="AGI per Return ($1000s) in Iowa City Commuting Zone in 2015",
 num_colors=5,
 county_zoom=ic_cz)
choro_agi_per_return
#Save map to the "output" folder
ggsave("output/ic_map.png")

